---
title: "Example Project Task 3"
author: "Ben Woodruff"
date: '2022-09-29'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro


## Calculutaions

When we plot the distribution of intensities after 2000 hours, we get the following plot. 

```{r}
rm(list=ls())
library(data4led)
dist <- led_time(2100)
hist(dist$percent_intensity,probability = TRUE)
```

For the function $f_0(L; a,b) = \frac{1}{b-a}$, recall that changing $a$ adjust the starting point on the left of the graph, and chaning $b$ adjusts the starting point on the right of the graph. The plot below illustrates this. 

```{r}
f0 <- function(x,a=0,b=1){
  # Make sure a < b when using this function.
  ifelse((a < x) & (x < b), 1/(b-a) + 0*x[(a < x) & (x < b)],NaN)
}

#Change these values as needed to compare plots. 
a1 <- 92
a2 <- 98

b1 <- 104
b2 <- 104

x <- seq(min(a1,a2),max(b1,b2),0.1)
y1 <- f0(x,a1,b1)
y2 <- f0(x,a2,b2)

xlimits = c(min(a1,a2)-2,max(b1,b2)+2)
ylimits = c(0,1)

par(mfrow=c(1,2),mar=c(2.5,2.5,2,0.25),oma=c(0,0,1,0))
plot(x,y1,type='l',xlim=xlimits,ylim=ylimits)
mtext(paste('a =',a1," and b=",b1), side = 3, line = 0)
plot(x,y2,type='l',xlim=xlimits,ylim=ylimits)
mtext(paste('a =',a2," and b=",b2), side = 3, line = 0)
mtext('Plot of f0',side=3,line=0,outer=TRUE)
```

Since the histogram starts at around 99.5, and ends after 103.5, let's use these for $a$ and $b$. This gives the graph below. 

```{r}
f0 <- function(x,a=0,b=1){
  # Make sure a < b when using this function.
  1/(b-a) + 0*x
}

a <- 99.5
b <- 103.5

x <- seq(a,b,0.01)
y <- f0(x,a=a,b=b)

par(mfrow=c(1,1),mar=c(2,2,3,0.25),oma=rep(0.5,4))
hist(dist$percent_intensity,
     probability = TRUE,
     xlim=c(98,105),
     ylim=c(0,0.8),
     main="Histogram of Lightbulb Intensities \n with fitted f0 function")
points(x,y,col=2, type = "l")
```

From the image above, the function $f_0$ doesn't appear to be a great fit, as it's flat, while the histogram is more bell shaped. 
